intro

### 2022-03-10 06_Paper/ER-ED/TheoreticalBackground.Rmd
Update Hypoth. 3b
comment on statistical testing and recomendation for alternative formulation of Hyp. 3
Hypoth. 5
added comment

* H3a) Subjective effort is greater after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
* H3b) The majority of participants re-uses the strategy that was least effortful for them.

@@

>>>>

* H3a) Subjective effort is greater after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
* H3b) The majority of participants re-uses the strategy that was least effortful for them. <!-- Könnt ihr diese Hypothese statistisch testen? Finde im 'Analysis Plan' nicht, wie ihr das testen möchtet, das muss dort noch erklärt werden. Mein Vorschlag für diese Hypothese: When having free choice, participants re-use the strategy with less subjective effort.-->

@@

<!-- Gibt es zu Hyp. 5 einen Abschnitt im 'Analysis Plan'? Das MLM? Ich schlage vor, dass der Analysis Plan streng nach den Hypothesen geordnet wird, dann ist es viel leichter zu lesen, zu verstehen und ihr vergesst auch nichts.-->
